Supplementary Material: District-level male medical and traditional circumcision coverage and unmet need in sub-Saharan Africa

### 2023-08-18 paper/supp_figs.tex
Updates from Overleaf

We identified 109 nationally representative household surveys conducted the study region  between 2002 and 2019. 
These included several major survey series, namely the Demographic and Health Surveys (DHS), AIDS Indicator Surveys (AIS) Population-based HIV Impact Assessment (PHIA) surveys, Multiple Indicator Cluster Surveys (MICS), and, in the case of South Africa, Human Sciences Research Council (HSRC) surveys \cite{dhs} \cite{ais} \cite{phia} \cite{hsrc2002} \cite{hsrc2008} \cite{hsrc2012} \cite{hsrc2017} \todo{include MICS reference}.
Data on self-reported circumcision status were available in 104 out of the total 109 surveys. 
\textbf{[Expand on reasons for exclusions]} \textbf{[Link in your survey figure]} \todo{done, what do you mean by "link in survey figure?"}
Excluded surveys lacked information on age at circumcision, which made it impossible to make inferences on circumcision under our time-to-event modelling framework. The surveys which were excluded on the basis of this requirement were the 2008 Botswana AIDS Impact Survey (BAIS) and 2013 BAIS surveys, the Central African Republic 2018 MICS survey and the 2014 and 2018 Guinea-Bissau MICS surveys \cite{bais2008} \cite{bais2013}.
For 5 countries, namely Liberia, Senegal, Niger, Guinea, and the DR Congo, information on circumcision type was not available in any surveys. Therefore, only MC could be estimated in these countries, and no inferences about circumcision type, whether MMC or TMC, could be made.
See figure 1 for a visual representation of the different survey providers for each country, as well as the sample size of each survey and the availability of circumcision type information. 
See table 1 for the full list of surveys for each country, and the circumcision information included in each survey.

>>>>

We identified 109 nationally representative household surveys conducted the study region  between 2002 and 2019. 
These included several major survey series, namely the Demographic and Health Surveys (DHS), AIDS Indicator Surveys (AIS) Population-based HIV Impact Assessment (PHIA) surveys, Multiple Indicator Cluster Surveys (MICS), and, in the case of South Africa, Human Sciences Research Council (HSRC) surveys \cite{dhs, ais, phia, hsrc2002, hsrc2008, hsrc2012, hsrc2017} \todo{include MICS reference}.
Data on self-reported circumcision status were available in 104 out of the total 109 surveys. 
\textbf{[Expand on reasons for exclusions]} \textbf{[Link in your survey figure]} \todo{done, what do you mean by "link in survey figure?"}
Excluded surveys lacked information on age at circumcision, which made it impossible to make inferences on circumcision under our time-to-event modelling framework. The surveys which were excluded on the basis of this requirement were the 2008 Botswana AIDS Impact Survey (BAIS) and 2013 BAIS surveys, the Central African Republic 2018 MICS survey and the 2014 and 2018 Guinea-Bissau MICS surveys \cite{bais2008, bais2013}.
For 5 countries, namely Liberia, Senegal, Niger, Guinea, and the DR Congo, information on circumcision type was not available in any surveys. Therefore, only MC could be estimated in these countries, and no inferences about circumcision type, whether MMC or TMC, could be made.
See figure 1 for a visual representation of the different survey providers for each country, as well as the sample size of each survey and the availability of circumcision type information. 
See table 1 for the full list of surveys for each country, and the circumcision information included in each survey.
